Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-09-21 doc/paper.tex
update of concept

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that is considered for solving. \fxnote{work in progress...}
    \end{comment}   
     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon). 
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we are looking for the number of points in D(P) that are visible from the given vertex $(|V(j)|)$. Based on this measure, we assign prices to the vertices. If |V(j)| is larger, the large is the price of the vertex $j$.
       \end{itemize}
     \section{Conclusions and Future Work}

>>>>

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that is considered for solving. \fxnote{work in progress...}
    \end{comment}

    \subsection{Hybrid Greedy + CPLEX}
        CPLEX will soon or later degrade in its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over interactions  and use CPLEX to make the (partial)  solution complete. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations and obtain a partial solution $C$ (therefore, $|C| = K$); 
        	\item Take solution $C$ and make it complete via. CPLEX model. 
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-problem which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$. 
        \end{enumerate}

       \noindent \textbf{Improvements of the above method.} The above method can serve as a basic iteration 
       of a more advanced techniques like ILP-LNS or CMSA. In this case, methods for destructing the solutions 
       has to be proposed.  Underlying idea could be:
       \begin{itemize}
       	    \item remove $N$ guards with the largest costs out of $C'$
       	    \item remove $N$ guards which have a higher amount of points from $D(P)$ covered by other guards, represented by the function
       	    \begin{align}
       	       ratio(i) = \frac{\sum_{v \in V, j \in V(i)} 1_{j \mbox{ is veasible from } v} }{|V(i)|}. 
       	    \end{align}
       \end{itemize}

     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$  as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon). 
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we are looking for the number of points in D(P) that are visible from the given vertex $(|V(j)|)$. Based on this measure, we assign prices to the vertices. If |V(j)| is larger, the large is the price of the vertex $j$.
       \end{itemize}
     \section{Conclusions and Future Work}
